Personalization and probabilities: impersonal propensities in online grocery shopping

### 2018-02-07 log.rmd
entered changes in section B,C,D

    - The section on limitations of association rule systems has been re-framed in the introduction/overview, and I've added some sentences at the beginning of the section explaining why attention to limitations is relevant to the main argument about probabilities. 

@@

>>>>

    - The section on limitations of association rule systems has been re-framed in the introduction/overview, and I've changed sentences at the close of the section explaining why attention to limitations is relevant to the main argument about probabilities. 

@@

## Wed 07 Feb 2018 09:53:49 GMT
- starting section B edits. Not too much to do here.  
- Section C -- only made a few changes; 
- Section D -- thinking I should combine this into the main section E? no, I didn't. But did do a bit of reframing
- Reached Section E (v) - platform experiments
